---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw3lm

<!-- badges: start -->
[![R-CMD-check](https://github.com/ziyuliu1999/hw3_lm/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ziyuliu1999/hw3_lm/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

<!-- badges: start -->
  [![Codecov test coverage](https://codecov.io/gh/ziyuliu1999/hw3_lm/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ziyuliu1999/hw3_lm?branch=main)
  <!-- badges: end -->

## Overview

hw3_lm is a R package created for the biostat625 homework 3. hw3_lm contains a function called `linear_regression(X, Y)`

## Installation

You can install the development version of hw3lm from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ziyuliu1999/hw3_lm")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hw3lm)
set.seed(1)
x = matrix(rnorm(3*100), nrow = 100, ncol = 3)
y = matrix(rnorm(1*100), nrow = 100, ncol = 1)
res = linear_regression(x, y)
```

We use `rnorm` to generate a $100 \times 3$ dimensional matrix as the predictors of the fitting model and generate a $100 \times 1$ dimensional matrix as the response of the fitting model. To make the code reproducible, let's set the seed to 1.

Here is the return of te `linear_regression` model. The first column is the coefficients estimate, the second column is the standard error of the corresponding coefficients, the third column is the t value of the corresponding coefficients, and the fourth column is the P-value of the coefficients. A same perfomance can be achieved via using the `summary(lm(y ~ x))$coefficients`

```{r}
res
```

