---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hw3lm)
library(Rcpp)
```

```{r}
cppFunction('
float sum_cpp(const std::vector<float> numbers) {
  float sum = 0;
  for (float number : numbers) {
    sum += number;
  }
  return(sum);
}')
```


```{r}
set.seed(1)
x = matrix(rnorm(3*100), nrow = 100, ncol = 3)
y = matrix(rnorm(1*100), nrow = 100, ncol = 1)
res = linear_regression(x, y)
```

We generated data using the `rnorm` function. X is a $100 \times 3$ dimensional matrix. In other words, we are gonna fit the model with three predictors. Y is a $100 \times 1$ dimensional matrix. 

```{r}
lm_res = lm(y ~ x)
```

```{r}
sum_res = summary(lm_res)$coefficients
```

Here is the result generated from `summary(lm(y ~ x))$coefficients`

```{r}
sum_res
```

Here is the result generated from our `linear_regression` code

```{r}
res
```

Here we can see the our result is same as the `summary(lm(y ~ x))$coefficients`, which is what we expected.

```{r}
all.equal(res, sum_res)
```

Here we can see that our code in total spend 469 ms and the original R package used 454 ms, which implies that our code is a little bit slower than the R original 

```{r}
bench::mark(our_code = linear_regression(x, y), lm_code = summary(lm(y ~ x))$coefficients)
```

We used the built-in data mtcars to test our model. With mpg as the response, disp, hp, drat, wt, and qsec are the predictors. 

We fit our model first.

```{r}
data("mtcars")
x_real = mtcars[, c(3, 4, 5, 6, 7)]
y_real = mtcars[, 1]
res_real = linear_regression(x_real, y_real)
```

Then we use the lm function to fit in the model.

```{r}
lm_real = summary(lm(mpg ~ disp + hp + drat + wt + qsec, data = mtcars))$coefficients
```



```{r}
all.equal(lm_real, res_real)
```

Our function's total time is 4ms slower than the built int R-package.

```{r}
bench::mark(our_code = linear_regression(x_real, y_real), lm_code = summary(lm(mpg ~ disp + hp + drat + wt + qsec, data = mtcars))$coefficients)
```
