---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hw3lm)
library(bench)
```

```{r}
set.seed(1)
x = matrix(rnorm(3*100), nrow = 100, ncol = 3)
y = matrix(rnorm(1*100), nrow = 100, ncol = 1)
res = linear_regression(x, y)
```

We generated data using the `rnorm` function. X is a $100 \times 3$ dimensional matrix. In other words, we are gonna fit the model with three predictors. Y is a $100 \times 1$ dimensional matrix. 

```{r}
lm_res = lm(y ~ x)
```

```{r}
sum_res = summary(lm_res)$coefficients
```

Here is the result generated from `summary(lm(y ~ x))$coefficients`

```{r}
sum_res
```

Here is the result generated from our `linear_regression` code

```{r}
res
```

Here we can see the our result is same as the `summary(lm(y ~ x))$coefficients`, which is what we expected.

```{r}
all.equal(res, sum_res)
```

Here we can see that our code in total spend 469 ms and the original R package used 454 ms, which implies that our code is a little bit slower than the R original 

```{r}
mark(our_code = linear_regression(x, y), lm_code = summary(lm(y ~ x))$coefficients)
```

